Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension

### 2018-05-29 EMNLP-demo-paper/intro.tex
update intro

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipeline}
 \vspace{-3mm}
 \caption{
 Perturbation-driven interrogation of the end-to-end models that follows the encoder, attention, and classifier structure. The user can generate small perturbation of the input (i.e., replacing synonyms, paraphrasing)
 }
 \vspace{-3mm}
\label{fig:modelPipeline}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipeline}
 \vspace{-3mm}
 \caption{
 Perturbation-driven interrogation of the end-to-end models that follow the encoder, attention, and classifier structure. The user can generate small perturbation of the input (i.e., replacing synonyms, paraphrasing), edit the attention, and observe the changes.
 }
 \vspace{-3mm}
\label{fig:modelPipeline}
\end{figure}
